---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# descriptiveStats

<!-- badges: start -->
<!-- badges: end -->

`DescriptiveStats` is a lightweight R package providing basic descriptive statistics functions with robust input validation and informative messaging. It is designed to handle common edge cases such as missing values, empty vectors, and non-numeric inputs gracefully.

## Installation

You can install the development version directly from GitHub:

```{r installation}
# install.packages("devtools") # if not already installed
# devtools::install_github("yifeng-wu/DescriptiveStats")
```

## Usage

```{r usage}
library(descriptiveStats)
x <- c(1, 2, 3, 4, 5)
```

**Arithmetic Mean**

```{r}
calc_mean(x)
```

**Median**

```{r}
calc_median(x)
```

**Statistical Mode (Most Frequent Value)**

```{r}
# Single mode
calc_mode(c(1, 2, 2, 3))

# Multiple modes (tie)
calc_mode(c(1, 1, 2, 2))

# All values unique (all returned)
calc_mode(c(1, 2, 3))
```

**First Quartile (Q1) and Third Quartile (Q3)**

```{r}
calc_q1(x)
calc_q3(x)
```

**Interquartile Range (IQR)**

```{r}
calc_iqr(x)
```

**Handling of NA (missing) values**
```{r}
calc_mean(c(x, NA))
```

